\chapter*{Decleration}
\addcontentsline{toc}{chapter}{Decleration}

I declare that the contents of this thesis derive from my own original research between January 2010 and November 2014, the period during which I was registered for the degree of Doctor of Philosophy at University of York.

Contributions from this thesis have been published in the following papers: 

\begin{itemize}

\item M. Ahmad and M. Oriol. Dirt Spot Sweeping Random strategy. \textit{Poster presentation in fourth York Doctoral Symposium (YDS 2011)}, York, UK. October 2011.

\item M. Ahmad and M. Oriol. Dirt Spot Sweeping Random strategy. In \textit{Proceedings of the International Conference on Software and Information Engineering (ICSIE)}, Singapore. Lecture Notes on Software Engineering, Volume 2(4), pp. 294-299, 2014.

Based on research described in Chapter~\ref{chap:DSSR} of the thesis.\\

\item M. Ahmad and M. Oriol. Automated Discovery of Failure Domain. In \textit{Proceedings of the International Conference on Software and Computer Applications (ICSCA)}, Paris, France. Lecture Notes on Software Engineering, Volume 1(3), pp. 289-294, 2014.

Based on research described in Chapter~\ref{chap:ADFD} of the thesis.\\

\item M. Ahmad and M. Oriol. ADFD$^+$: An Automatic Testing Technique for Finding and Presenting Failure domains. In \textit{Proceedings of the International Conference on Software and Information Engineering (ICSIE)}, Singapore. Lecture Notes on Software Engineering, Volume 2(4), pp. 331-336, 2014.

Based on research described in Chapter~\ref{chap:ADFD+} of the thesis.\\

\item M. Ahmad and M. Oriol. Evaluation of ADFD and ADFD$^+$ techniques. In \textit{Proceedings of Seventh York Doctoral Symposium (YDS 2014)}, York, UK. October 2014. 

Based on research described in Chapter~\ref{chap:Evaluation} of the thesis.

\end{itemize}

%\end{declaration}