% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments


Several people have contributed to the completion of my PhD dissertation. However, the most prominent personality deserving due recognition is my worthy supervisor, Dr. Manuel Oriol. Thank you Manuel for your endless help, valuable guidance, constant encouragement, precious advice, sincere and affectionate attitude.

I thank my assessor Prof. John Clark for his constructive feedback on my various reports and presentations. I am also thankful and highly indebted to Prof. Richard Paige for his generous help, cooperation and guidance during my research at the University of York.

Special thanks to my father Prof. Mushtaq A. Mian who provided a conducive environment, valuable guidance and crucial support at all levels of my educational career and my very beloved mother whose love, affection and prayers have been my most precious assets. Also I am thankful to my elder brothers Dr. Ashfaq, Dr. Aftab, Dr. Ishaq, Dr. Afaq and my sister Dr. Haleema who have been the source of inspiration for me to pursue higher studies. My immediate younger brother Dr. Ilyas and my younger sister Ayesha studying in the UK, deserve recognition for their help, well wishes and moral support. Last but not the least I am very thankful to my dear wife Dr. Munazza for her company, help and cooperation throughout my stay at York.

I was funded by Departmental Overseas Research Scholarship (DORS), a financial support awarded to overseas students on the basis of outstanding academic ability and research potential. I am truly grateful to the Department of Computer Science for financial support that allowed me to concentrate on my research.



\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
