\begin{acknowledgements}
The years I spent working on my PhD degree at the University of York have undoubtedly been some of the most joyful and rewarding in my academic career. The institution provided me with everything I need to thrive: challenging research problems, excellent company, and a supportive environment. I am deeply grateful to the people who shared this experience with me and to those who made it possible. 

Several people have contributed to the completion of my PhD dissertation. However, the most prominent personality deserving due recognition is my worthy advisor, Dr. Manuel Oriol. Thank you Manuel for your endless help, valuable guidance, constant encouragement, precious advice, sincere and affectionate attitude.

I thank my assessor prof. John Clark for his constructive feedback on my various reports and presentations. I am also thankful and highly indebted to Prof. Richard Paige for his generous help, cooperation and guidance during my research at the University of York.

Special thanks to my father Prof. Dr. Mushtaq who provided a conducive environment, valuable guidance and crucial support at all levels of my educational career and my very beloved mother whose love, affection and prayers have been my most precious assets. Also I am thankful to my brothers Dr. Ashfaq, Dr. Aftab, Dr. Ishaq, Dr. Afaq, and Dr. Ilyas who have been the source of inspiration for me to pursue higher studies. Last but not the least I am very thankful to my dear wife Dr. Munazza for her company, help and cooperation throughout my stay at York.

I was funded by Departmental Overseas Research Scholarship (DORS), a financial support awarded to overseas students on the basis of outstanding academic ability and research potential. I am truly grateful to the Department of Computer Science for financial support that allowed me to concentrate on my research.

\end{acknowledgements}